Technical Report

### 2018-03-20 fully-abstract-comp/technical-report.tex
Fix small latex issue: \dom does not take a latex argument.
a couple more changes related to retptrc/d change
updated execCond and sealed capability case in LR to have a linera and normal case
Minor fixes.
Small fix.
minor code region changes
Minor fixes in Hcodesigma.
Require current address of stack pointer to be correct value.
Some changes to the code region.

\subsection{Programs and contexts}
\begin{definition}
  \label{def:self-contained}
  \begin{itemize}
  \item We say that a memory segment $\ms$ and a list of words $\bar{w}$
    are self-contained iff
  \[
    \forall w \in \bar{w} \ldotp w \in \Caps \lor w = \stkptr{\_,\_,\_,\_} \Rightarrow \range{w} \subseteq \dom(\ms)
  \]
  and
  \begin{multline*}
    \forall a \in \dom(\ms) \ldotp\\
    (\ms(a) \in Caps \lor \ms(a) = \stkptr{\_,\_,\_,\_}) \Rightarrow \range{\ms(a)} \subseteq \dom{\ms}
  \end{multline*}
  \item We say that a memory segment $\ms$ and a list of capabilities $\bar{c}$ are self contained with slack $\ms_s$ iff
  \[
    \forall c \in \bar{c} \ldotp \range{c} \subseteq \dom{\ms \cup \ms_s}
  \]
  and
  \begin{multline*}
    \forall a \in \dom(\ms) \ldotp\\
    (\ms(a) \in Caps \lor \ms(a) = \stkptr{\_,\_,\_,\_}) \Rightarrow \range{\ms(a)} \subseteq \dom{\ms \cup \ms_s}
  \end{multline*}
\end{itemize}
\end{definition}

@@

\section{Logical Relation}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} was used to indicate source language specific parts of definitions.
\subsection{Worlds}
\[
  \World = \Worldh \times \Worlds \times \Worldfs
\]
with $\Worlds$, $\Worldh$, and $\Region$ defined as follows
\[
  \Worldh = \RegionName \parfun (\Regions + \Regionh)
\]
and
\[
  \Worlds = \RegionName \parfun (\Regions \times \SealableCaps)
\]
and
\[
  \Worldfs = \RegionName \parfun \Regions
\]
where $\RegionName = \nats$.
\begin{multline*}
  \Regionh = 
  \{\pure \} \times \State \times \Rels \times\\
  (\State \fun \World \monnefun \URel{\MemSeg^2}) \times \\
  (\State \fun \Seal \parfun \World \monnefun \URel{\Caps \times \SealableCaps})
\end{multline*}
and
\[
  \Regions = \left\{
  \begin{array}{l}
    \{\spatial \} \times \State \times \Rels \times (\State \fun \World \monnefun \URel{\MemSeg^2}) \uplus \\
    \{\spatialo \} \times \State \times \Rels \times (\State \fun \World \monnefun \URel{\MemSeg^2})\uplus \\ 
    \{\revoked\}
  \end{array} \right.
\]
where $\spatial$ and $\spatialo$ are regions governing segments of memory addressed by linear capabilities.
$\spatialo$ signifies that this region is addressable.
$\spatial$ signifies that the region is not owned and can thus not be addressed.
At the same time it signifies that if something else addresses it, it is a $\linear$ capability.
Finally, $\pure$ signifies that the region is only addressed by non-linear capabilities.
Notice that no region allows for both linear and non-linear capabilities to address it.
Notice also that $\pure$ regions have an additional component that allows them to claim ownership of part of the address space of seals and impose a relational invariant on everything signed with those seals.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{\vsc_S},\vsc_T)} \in \lrp(W) \wedge \\
      \exists r \in \dom(\pwheap)\ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand \\
      \quad \stpair[.]{\vsc_S}{\vsc_T} \in H_\sigma \; s \; \sigma \; W\wedge \\
      \quad \forall W' \future W, W_o, n' < n, \stpair[.]{\vsc_S'}{\vsc'_T} \in H_\sigma \; s \; \sigma \; W_o \ldotp \\
      \qquad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o) 
      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand H_\sigma\; s \; \sigma \nequal \lrv
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall n' < n, W' \future W, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr], W'' \ldotp\\
      \qquad \npair[n']{[\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)}]} \in \lrp(W' \oplus W'') \Rightarrow \\
      \quad \qquad \npair[n']{\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)}} \in \lre(W' \oplus W'')
    \end{array}
    \right\}
\]

@@

\[
  \codereg{\ta,\sigma_\baddr,\sigma_\eaddr,\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code,H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code)
\]

\[
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \sigma_\eaddr \; \code \; s \; \hat{W} = \{\npair{(\code,\code)} | \dom(\code) = [\aaddr,\baddr] \tand \code(a) = \seal{\sigma_\baddr,\sigma_\baddr,\sigma_\eaddr}\}
\]
\lau{19-03-2018: Add the link capability to the above? code in ta?}
\[
  H^\mathrm{code}_\sigma \; \ta \; s \; \sigma \; \hat{W} = 
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\sealed{\sigma,\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1)},\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen]-1)} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}

    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\sealed{\sigma,\retptrd(\baddr,\eaddr)},\\((\rx,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr')) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen]-1)} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \aaddr = \aaddr' + \calllen \tand \\
        \quad \sigma = \sigma_\baddr + o \tand\\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}
      \sealed{\sigma,\vsc}, \vsc' \endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \sigma \in [\sigma_\baddr,\sigma_\eaddr] \tand\\
        (\dom(\code) \cup \ta \neq \emptyset \tand \npair{\vsc,\vsc'} \in \lrv \; W) \tor \\
        \text{not a call}
      \end{array}
    \end{array}
      \right\}
  \end{array}
\]

>>>>

\subsection{Programs and contexts}
\begin{definition}
  \label{def:self-contained}
  \begin{itemize}
  \item We say that a memory segment $\ms$ and a list of words $\bar{w}$
    are self-contained iff
  \[
    \forall w \in \bar{w} \ldotp w \in \Caps \lor w = \stkptr{\_,\_,\_,\_} \Rightarrow \range{w} \subseteq \dom(\ms)
  \]
  and
  \begin{multline*}
    \forall a \in \dom(\ms) \ldotp\\
    (\ms(a) \in Caps \lor \ms(a) = \stkptr{\_,\_,\_,\_}) \Rightarrow \range{\ms(a)} \subseteq \dom(\ms)
  \end{multline*}
  \item We say that a memory segment $\ms$ and a list of capabilities $\bar{c}$ are self contained with slack $\ms_s$ iff
  \[
    \forall c \in \bar{c} \ldotp \range{c} \subseteq \dom(\ms \cup \ms_s)
  \]
  and
  \begin{multline*}
    \forall a \in \dom(\ms) \ldotp\\
    (\ms(a) \in Caps \lor \ms(a) = \stkptr{\_,\_,\_,\_}) \Rightarrow \range{\ms(a)} \subseteq \dom(\ms \cup \ms_s)
  \end{multline*}
\end{itemize}
\end{definition}

@@

\section{Logical Relation}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} was used to indicate source language specific parts of definitions.
\subsection{Worlds}
\[
  \World = \Worldh \times \Worlds \times \Worldfs
\]
with $\Worlds$, $\Worldh$, and $\Region$ defined as follows
\[
  \Worldh = \RegionName \parfun (\Regions + \Regionh)
\]
and
\[
  \Worlds = \RegionName \parfun (\Regions \times \SealableCaps)
\]
and
\[
  \Worldfs = \RegionName \parfun \Regions
\]
where $\RegionName = \nats$.
\begin{multline*}
  \Regionh = 
  \{\pure \} \times \State \times \Rels \times\\
  (\State \fun \World \monnefun \URel{\MemSeg^2}) \times \\
  (\State \fun \Seal \parfun \World \monnefun \URel{\SealableCaps \times \SealableCaps})
\end{multline*}
and
\[
  \Regions = \left\{
  \begin{array}{l}
    \{\spatial \} \times \State \times \Rels \times (\State \fun \World \monnefun \URel{\MemSeg^2}) \uplus \\
    \{\spatialo \} \times \State \times \Rels \times (\State \fun \World \monnefun \URel{\MemSeg^2})\uplus \\ 
    \{\revoked\}
  \end{array} \right.
\]
where $\spatial$ and $\spatialo$ are regions governing segments of memory addressed by linear capabilities.
$\spatialo$ signifies that this region is addressable.
$\spatial$ signifies that the region is not owned and can thus not be addressed.
At the same time it signifies that if something else addresses it, it is a $\linear$ capability.
Finally, $\pure$ signifies that the region is only addressed by non-linear capabilities.
Notice that no region allows for both linear and non-linear capabilities to address it.
Notice also that $\pure$ regions have an additional component that allows them to claim ownership of part of the address space of seals and impose a relational invariant on everything signed with those seals.

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \;\middle|\; i \in \ints \right\}\cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \;\middle| \;
    \begin{array}{l}
      \npair{(\src{\vsc_S},\vsc_T)} \in \lrp(W) \wedge \\
      \exists r \in \dom(\pwheap)\ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand \\
      \quad \stpair[.]{\vsc_S}{\vsc_T} \in H_\sigma \; s \; \sigma \; W\wedge \\
      \quad (\isLinear{\vsc_1} \Rightarrow \forall W' \future W, W_o, n' < n, \stpair[.]{\vsc_S'}{\vsc'_T} \in H_\sigma \; s \; \sigma \; W_o \ldotp \\
      \qquad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o)) \wedge \\
      \quad (\nonLinear{\vsc_1} \Rightarrow \forall W' \future \purePart{W}, W_o, n' < n, \stpair[.]{\vsc_S'}{\vsc'_T} \in H_\sigma \; s \; \sigma \; W_o \ldotp \\
      \qquad \npair[n']{\src{\vsc_S},\src{\vsc_S'},\vsc_T,\vsc_T'} \in \lrexj(W'\oplus W_o))

      % This case was never used (?) so it is not necessary.
      % \wedge \\
      % \quad \npair[n']{\src{\vsc_S'},\src{\vsc_S},\vsc_T',\vsc_T} \in \lrexj(W' \oplus W_o)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\seal{\sigma,\sigma_\baddr,\sigma_\eaddr}},\\ \seal{\sigma,\sigma_\baddr,\sigma_\eaddr} \endarray \right)} 
    \; \middle| \;
    \exists r \in \dom(\pwheap) \ldotp \pwheap(r) = (\pure,s,\_,\_,\_,H_\sigma) \tand H_\sigma\; s \; \sigma \nequal \lrv
    \right\} \cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\;
    \begin{array}{l}
      \npair{(\src{\stkptr{\perm,\baddr,\eaddr,\aaddr}}, ((\perm,\linear),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l}
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackReadCond{W} \wedge \\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \stackWriteCond{W}
      \end{array}
    \end{array}
    \right\} \cup \\
%
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{((\perm,\lin),\baddr,\eaddr,\aaddr)},\\ ((\perm,\lin),\baddr,\eaddr,\aaddr) \endarray \right)} \;\middle|\; 
    \begin{array}{l}
      \npair{(\src{((\perm,\lin),\baddr,\eaddr,\aaddr)}, ((\perm,\lin),\baddr,\eaddr,\aaddr))} \in \lrp(W) \wedge \\
      \begin{array}{r l l }
        \perm \in \readAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \readCond{\lin,W} \wedge\\
        \perm \in \writeAllowed{} &\Rightarrow& \npair{(\baddr,\eaddr)} \in \writeCond{\lin,W} \wedge\\
        % we are excluding rwx pointers.
        \perm \neq \rwx \wedge \\
        % \perm = \rwx &\Rightarrow& \array[t]{l}\npair{(\{\rwx,\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge \\
        %                            \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W} \endarray\\
        \perm = \rx &\Rightarrow& \array[t]{l}\npair{(\{\rx\},\baddr,\eaddr)} \in \execCond{\lin,W} \wedge\\
                                  \npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}\endarray
      \end{array}
    \end{array}
    \right\}
  \end{array}
\]

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
Note: this new version of execCond uses the expression relation for regular jumps since it expresses the validity of jumping to an address pointed to by an executable capability. 
\[
  \execCond{\lin,W} = \left\{ \npair{(S_\perm,\baddr,\eaddr)} \middle|
    \begin{array}{l}
      \forall W_l \ldotp\\
      \quad ((W_l = \purePart{W} \wedge \lin = \normal) \vee (W_l = W \wedge \lin = \linear)) \wedge\\
      \quad \forall n' < n, W' \future W_l, \perm \in S_\perm, \aaddr \in [\baddr,\eaddr] \ldotp\\
      \quad \qquad \npair[n']{[\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)}]} \in \lrp(W') \Rightarrow \\
      \qquad \qquad \npair[n']{\stpair[.]{((\perm,\lin),\baddr,\eaddr,\aaddr)}{((\perm,\lin),\baddr,\eaddr,\aaddr)}} \in \lre(W')
    \end{array}
    \right\}
\]

@@

\[
  \codereg{\ta,\overline{\sigma_{\mathrm{ret}}},\overline{\sigma_{\mathrm{clos}}},\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code,H^\mathrm{code}_\sigma \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code)
\]

\[
  H^\mathrm{code} \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code \; s \; \hat{W} = \left\{
    \npair{(\code,\code)} \mid
  \begin{multlined}
    \dom(\code) = [\aaddr,\baddr] \tand (\overline{\sigma_{\mathrm{ret}}} \cup \overline{\sigma_{\mathrm{clos}}}) = [\sigma_\baddr,\sigma_\eaddr] \tand \\
    \code(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}
  \end{multlined}
  \right\}
\]
\lau{19-03-2018: Add the link capability to the above? code in ta?}
\[
  H^\mathrm{code}_\sigma \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code \; s \; \sigma \; \hat{W} = 
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \in \overline{\sigma_{\mathrm{ret}}}\tand\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \sigma = \sigma_\baddr + o \in \overline{\sigma_{\mathrm{ret}}}\tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma \in \overline{\sigma_{\mathrm{clos}}} \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{\vsc,\vsc'} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\]
